---
title: "analysis-household-income"
author: "xrw"
date: "5/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

```

## Set up

Some of the older data is in dta (Stata) format, so we need `foreign`. Additionally, I'm importing reticulate bc there's some python packages I like to use...

```{r}

library(tidyr)
library(tidyverse)
library(dplyr)
library(foreign)
library(reticulate)
library(haven)
#use_condaenv('numlinalg')
#numpy <- import('numpy')
#rasterio <- import('rasterio')
#pandas <- import('pandas')
#comment out python stuff for now

```


```{r dataimport}


chips_rur_1988 <- read_dta('data/1988/09836-0002-Data.dta')
chips_rur_1995 <- read_tsv('data/1995/DS0002/03012-0002-Data.tsv')
chips_rur_2002<- read_tsv('data/2002/DS0006/21741-0006-Data.tsv')
chips_rur_2007abc <- read_dta('data/2007 (2008)/RHS_w1_abc.dta')
chips_rur_2007d <- read_dta('data/2007 (2008)/RHS_w1_d.dta')
chips_rur_2007e1 <- read_dta('data/2007 (2008)/RHS_w1_e1.dta')
chips_rur_2007e2 <- read_dta('data/2007 (2008)/RHS_w1_e2.dta')
chips_rur_2007e3 <- read_dta('data/2007 (2008)/RHS_w1_e3.dta')
chips_rur_2007e4 <- read_dta('data/2007 (2008)/RHS_w1_e4.dta')
chips_rur_2007hhiexp <- read_dta('data/2007 (2008)/CHIP2007_income_and_expenditure_20150408.dta')
chips_rur_2008abc <- read_dta('data/2008 (2009)/RHS_w2_abc.dta')
chips_rur_2008d <- read_dta('data/2008 (2009)/RHS_w2_d.dta')
chips_rur_2008e <- read_dta('data/2008 (2009)/RHS_w2_e.dta')
chips_rur_2008f <- read_dta('data/2008 (2009)/RHS_w2_f.dta')
chips_rur_2008hgsg <- read_dta('data/2008 (2009)/RHS_w2_hgsg.dta')
chips_rur_2008hijk <- read_dta('data/2008 (2009)/RHS_w2_hijk.dta')
chips_rur_2008vill <- read_dta('data/2008 (2009)/RHS_w2_vill.dta')

chips_rur_2013 <- read_dta('data/2013/CHIP2013_rural_household_f_income_asset.dta')


```


## The data itself 

We have lots of data but none of it is really consistent. I guess they changed the survey at some point.

For 1988, income column: 
TOVIL <- Income from TVE, 99999999 is NA
WELF <- INcome from welfare fund
NETI <- net income from economic associations
GROST <- gross income from farming
GSIDEI <- income from non-agricultural activities
INPS <- income from non-productive services
IMONE <- income from government + collectives
HNET88 <- Net household income 1988 
LAT <- Total cultivated land, unit: mu =1/6 acre or 1/15 ha
X7 <- pork consumption
COUNTY <- county 
VHPFP <- fixed production assets, Value of family's fixed productive assets at end of 1988 (yuan)
EFP88 <- Total household expenditures on productive operations 

Examine 1988 data. 

Let's use: 
- Net household income
- Land cultivated
- Number of rooms in house 
- fixed production assets, Value of family's fixed productive assets
- Total household expenditures on productive operations


## Other years


## 1995 columns:
B601 <- net income in 1993
B602 <- net income in 1995
B801 <- Land cultivated 
B1001 <- Number of rooms
B804_1 <- fixed production assets, Value of family's fixed productive assets
B7130 <- Total household expenditures on productive operations

## 2002
?? unclear on why data for 2002 is so bad
P1_63 <- 


## 2008 (2009)
KO1 <- The production asset at the end of 2008
H01 <- cultivated land in mu 


## 2013 



```{r}
library(naniar)

# 99999999 is NA


chips_rur_1988_filt <- chips_rur_1988 %>% filter(HNET88 != 99999999, LAT != 999.9, HHO != 99, VHPFP != 99999, EFP88 != 99999999 ) 
```

```{r, echo=FALSE}
plot(chips_rur_1988_filt$HNET88, chips_rur_1988_filt$LAT)
plot(chips_rur_1988_filt$HHO, chips_rur_1988_filt$HNET88)
plot(chips_rur_1988_filt$VHPFP, chips_rur_1988_filt$HNET88)


labelDataset <- function(data) {
  correctLabel <- function(x) {

    if(!is.null(attributes(x)$labels)) {
      class(attributes(x)$labels) <- typeof(x)
    }
    return(x)
  }
  for(i in colnames(data)) {
    data[, i] <- correctLabel(data[, i])
  }
  return(data)
}


outlier_values <- boxplot.stats(chips_rur_1988_filt$HNET88)$out  # outlier values.
lm(HNET88~LAT, data=chips_rur_1988_filt)


#labelDataset(chips_rur_1988_filt)

chips_rur_1988_filt %>%
  split(.$COUNTY)

```





```{r}


```

```{r}

cr2007 <- read_dta('data/2007 (2008)/name_id_and_village_id_20151010.dta')
```

