---
title: "spot analysis of taobao village sites"
author: "Xiaowei Wang"
output: github_document
---

## Spot analysis of taobao village sites

spot analysis of taobao village sites and villages sites that are not taobao villages

```{r}

library(mapview)      #interactive maps, raster + vector layers
library(raster)       #Main raster library
library(tidyverse)    #our old friend
library(sf)           #to work with simple features data
library(dplyr)

```

## Read in and get some stats
```{r}

lbc2014 <- brick('data/lbc-raster-cropped/lbc_2014_cropped.tif')
lbc2015 <- brick('data/lbc-raster-cropped/lbc_2015_cropped.tif')
lbc2016 <- brick('data/lbc-raster-cropped/lbc_2016_cropped.tif')
lbc2017 <- brick('data/lbc-raster-cropped/lbc_2017_cropped.tif')

lbc2014
lbc2015
lbc2016
lbc2017
#12 band data from tif

plotRGB(lbc2014, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
        main = "Landsat True Color Composite lbc 2014")

# plotRGB(lbc2015, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite lbc2015")
# 
# plotRGB(lbc2016, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite lbc2016")
# 
# plotRGB(lbc2017, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite lbc2017")
```


##compute ndvi for LBC
```{r}
NDVI <- function(img, i, k) {
   bi <- img[[i]]
   bk <- img[[k]]
   vi <- (bk - bi) / (bk + bi)
   return(vi)
}
```


##function for NDBI
```{r}
NDBI <- function (img, w, n) {
  bw <- img[[w]]
  bn <- img[[n]]
  vn <- (bw - bn) / (bw + bn)
}
```

```{r}
# For landsat 8, NIR is 5, red is 4.
ndvilbc_2014 <- NDVI(lbc2014, 4, 5)
ndvilbc_2015 <- NDVI(lbc2015, 4 , 5)
ndvilbc_2016 <- NDVI(lbc2016, 4, 5)
ndvilbc_2017 <- NDVI(lbc2017, 4, 5)


ndbilbc_2014 <- NDBI(lbc2014, 7, 5)
ndbilbc_2015 <- NDBI(lbc2015, 7 , 5)
ndbilbc_2016 <- NDBI(lbc2016, 7, 5)
ndbilbc_2017 <- NDBI(lbc2017, 7, 5)




```


```{r}
plot(ndvilbc_2014, col = rev(terrain.colors(30)), main = 'NDVI lbc2014')
plot(ndvilbc_2015, col = rev(terrain.colors(30)), main = 'NDVI lbc2015')
 plot(ndvilbc_2016, col = rev(terrain.colors(30)), main = 'NDVI lbc2016')
 plot(ndvilbc_2017, col = rev(terrain.colors(30)), main = 'NDVI lbc2017')


# view distribution of NDVI values
# hist(ndvilbc_2014,
#   main = "NDVI: Distribution of pixels\n Landsat 2014 Libeicun",
#   col = "springgreen",
#   xlab = "NDVI lbc2014")
# 


```


```{r}

plot(ndbilbc_2014, col = rev(terrain.colors(30)), main = 'NDBI lbc2014')
# plot(ndbilbc_2015, col = rev(terrain.colors(30)), main = 'NDBI lbc2015')
# plot(ndbilbc_2016, col = rev(terrain.colors(30)), main = 'NDBI lbc2016')
# plot(ndbilbc_2017, col = rev(terrain.colors(30)), main = 'NDBI lbc2017')

```
## Calculate average NDVI as a time series

```{r}
ndvi_lbc_stack <- stack(ndvilbc_2014,ndvilbc_2015,ndvilbc_2016, ndvilbc_2017)
#names(ndvi_lbc_stack) <- c(2014,2015,2016,2017)
avg_ndvi_lbc <- cellStats(ndvi_lbc_stack, mean)

avg_ndvi_lbc <- as_tibble(avg_ndvi_lbc)
# add a site column to our data


# add a "year" column to our data
avg_ndvi_lbc$'year' <- c(2014,2015,2016,2017)
hist(ndvi_lbc_stack)

avg_ndvi_lbc <- avg_ndvi_lbc[c("year", "value")]
avg_ndvi_lbc = rename(avg_ndvi_lbc, `meanndvi` = value)
# avg_ndvi_lbc

ggplot(data = avg_ndvi_lbc, aes(x=year, y=meanndvi)) +
  geom_point()

```

### Calculate average NDBI as a time series

```{r}

ndbi_lbc_stack <- stack(ndbilbc_2014,ndbilbc_2015,ndbilbc_2016, ndbilbc_2017)
#names(ndbi_lbc_stack) <- c(2014,2015,2016,2017)
avg_ndbi_lbc <- cellStats(ndbi_lbc_stack, mean)

avg_ndbi_lbc <- as_tibble(avg_ndbi_lbc)
# add a site column to our data


# add a "year" column to our data
avg_ndbi_lbc$'year' <- c(2014,2015,2016,2017)
hist(ndbi_lbc_stack)

avg_ndbi_lbc <- avg_ndbi_lbc[c("year", "value")]
avg_ndbi_lbc = rename(avg_ndbi_lbc, `meanndbi` = value)
# avg_ndbi_lbc

ggplot(data = avg_ndbi_lbc, aes(x=year, y=meanndbi)) +
  geom_point()

```



## NDVI for non taobao village, 安徽省程楼村, Chengloucun

```{r}

clc2014 <- brick('data/clc/clc_2014.tif')
clc2015 <- brick('data/clc/clc_2015.tif')
clc2016 <- brick('data/clc/clc_2016.tif')
clc2017 <- brick('data/clc/clc_2017.tif')
clc2014nl <- brick('data/clc/clc_2014_nlviirs.tif')


#12 band data from tif
plotRGB(clc2014, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
        main = "Landsat True Color Composite clc 2014")

# plotRGB(clc2015, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite clc2015")
# 
# plotRGB(clc2016, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite clc2016")

plotRGB(clc2017, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
        main = "Landsat True Color Composite clc2017")

ndviclc_2014 <- NDVI(clc2014, 4, 5)
ndviclc_2015 <- NDVI(clc2015, 4 , 5)
ndviclc_2016 <- NDVI(clc2016, 4, 5)
ndviclc_2017 <- NDVI(clc2017, 4, 5)

```

```{r}
plot(clc2014nl, col = gray.colors(10, start = 0, end = 1, gamma = 2.2, alpha = NULL))
plot(ndviclc_2014, col = rev(terrain.colors(30)), main = 'NDVI clc2014')
# plot(ndviclc_2015, col = rev(terrain.colors(30)), main = 'NDVI clc2015')
# plot(ndviclc_2016, col = rev(terrain.colors(30)), main = 'NDVI clc2016')
# plot(ndviclc_2017, col = rev(terrain.colors(30)), main = 'NDVI clc2017')
# 


ndvi_clc_stack <- stack(ndviclc_2014,ndviclc_2015,ndviclc_2016, ndviclc_2017)
#names(ndvi_clc_stack) <- c(2014,2015,2016,2017)
avg_ndvi_clc <- cellStats(ndvi_clc_stack, mean)

avg_ndvi_clc <- as_tibble(avg_ndvi_clc)
# add a site column to our data


# add a "year" column to our data
avg_ndvi_clc$'year' <- c(2014,2015,2016,2017)
hist(ndvi_clc_stack)

avg_ndvi_clc <- avg_ndvi_clc[c("year", "value")]
avg_ndvi_clc = rename(avg_ndvi_clc, `meanndvi` = value)
# avg_ndvi_clc

ggplot(data = avg_ndvi_clc, aes(x=year, y=meanndvi)) +
  geom_point()

```

## NDVI for a Taobao village, 浙江省马丁村 Madingcun which was implemented as a Taobao village in 2015
```{r}

mdc2014 <- brick('data/mdc/mdc_2014.tif')
mdc2015 <- brick('data/mdc/mdc_2015.tif')
mdc2016 <- brick('data/mdc/mdc_2016.tif')
mdc2017 <- brick('data/mdc/mdc_2017.tif')
mdc2014nl <- brick('data/mdc/mdc_2014_nlviirs.tif')

mdc2014

#12 band data from tif



ndvimdc_2014 <- NDVI(mdc2014, 4, 5)
ndvimdc_2015 <- NDVI(mdc2015, 4 , 5)
ndvimdc_2016 <- NDVI(mdc2016, 4, 5)
ndvimdc_2017 <- NDVI(mdc2017, 4, 5)

```

```{r}
plotRGB(mdc2014, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
        main = "Landsat True Color Composite mdc 2014")

# plotRGB(mdc2015, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite mdc2015")
# 
# plotRGB(mdc2016, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite mdc2016")
# 
# plotRGB(mdc2017, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite mdc2017")
plot(ndvimdc_2014, col = rev(terrain.colors(30)), main = 'NDVI mdc2014')
# plot(ndvimdc_2015, col = rev(terrain.colors(30)), main = 'NDVI mdc2015')
# plot(ndvimdc_2016, col = rev(terrain.colors(30)), main = 'NDVI mdc2016')
# plot(ndvimdc_2017, col = rev(terrain.colors(30)), main = 'NDVI mdc2017')
# 


ndvi_mdc_stack <- stack(ndvimdc_2014,ndvimdc_2015,ndvimdc_2016, ndvimdc_2017)
#names(ndvi_mdc_stack) <- c(2014,2015,2016,2017)
avg_ndvi_mdc <- cellStats(ndvi_mdc_stack, mean)

avg_ndvi_mdc <- as_tibble(avg_ndvi_mdc)
# add a site column to our data


# add a "year" column to our data
avg_ndvi_mdc$'year' <- c(2014,2015,2016,2017)
hist(ndvi_mdc_stack)

avg_ndvi_mdc <- avg_ndvi_mdc[c("year", "value")]
avg_ndvi_mdc = rename(avg_ndvi_mdc, `meanndvi` = value)
# avg_ndvi_mdc

ggplot(data = avg_ndvi_mdc, aes(x=year, y=meanndvi)) +
  geom_point()

```


## Try another non-taobao village, Zizhucun

```{r}

zzc2014 <- brick('data/zzc/zzc_2014.tif')
zzc2015 <- brick('data/zzc/zzc_2015.tif')
zzc2016 <- brick('data/zzc/zzc_2016.tif')
zzc2017 <- brick('data/zzc/zzc_2017.tif')

zzcnl_2014 <- brick('data/zzc/zzc_2014_nlviirs.tif')
zzcnl_2015 <- brick('data/zzc/zzc_2015_nlviirs.tif')
zzcnl_2016 <- brick('data/zzc/zzc_2016_nlviirs.tif')
zzcnl_2017 <- brick('data/zzc/zzc_2017_nlviirs.tif')



#12 band data from tif



ndvizzc_2014 <- NDVI(zzc2014, 4, 5)
ndvizzc_2015 <- NDVI(zzc2015, 4 , 5)
ndvizzc_2016 <- NDVI(zzc2016, 4, 5)
ndvizzc_2017 <- NDVI(zzc2017, 4, 5)

```

```{r}

# plotRGB(zzc2014, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite zzc 2014")
# 
# plotRGB(zzc2015, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite zzc2015")
# 
# plotRGB(zzc2016, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite zzc2016")
# 
# plotRGB(zzc2017, r = 4, g = 3, b = 2, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite zzc2017")
raster::plot(zzcnl_2014, col = gray.colors(10, start = 0, end = 1, gamma = 2.2, alpha = NULL))
# raster::plot(zzc2015nl, col = gray.colors(10, start = 0, end = 1, gamma = 2.2, alpha = NULL))
# raster::plot(zzc2016nl, col = gray.colors(10, start = 0, end = 1, gamma = 2.2, alpha = NULL))
# raster::plot(zzc2017nl, col = gray.colors(10, start = 0, end = 1, gamma = 2.2, alpha = NULL))


plot(ndvizzc_2014, col = rev(terrain.colors(30)), main = 'NDVI zzc2014')
# plot(ndvizzc_2015, col = rev(terrain.colors(30)), main = 'NDVI zzc2015')
# plot(ndvizzc_2016, col = rev(terrain.colors(30)), main = 'NDVI zzc2016')
# plot(ndvizzc_2017, col = rev(terrain.colors(30)), main = 'NDVI zzc2017')
# 


ndvi_zzc_stack <- stack(ndvizzc_2014,ndvizzc_2015,ndvizzc_2016, ndvizzc_2017)
nl_zzc_stack <- stack(zzcnl_2014,zzcnl_2015,zzcnl_2016, zzcnl_2017)

#names(ndvi_zzc_stack) <- c(2014,2015,2016,2017)
avg_ndvi_zzc <- cellStats(ndvi_zzc_stack, mean)

avg_ndvi_zzc <- as_tibble(avg_ndvi_zzc)
# add a site column to our data


# add a "year" column to our data
avg_ndvi_zzc$'year' <- c(2014,2015,2016,2017)
hist(ndvi_zzc_stack)

avg_ndvi_zzc <- avg_ndvi_zzc[c("year", "value")]
avg_ndvi_zzc = rename(avg_ndvi_zzc, `meanndvi` = value)
# avg_ndvi_zzc

ggplot(data = avg_ndvi_zzc, aes(x=year, y=meanndvi)) +
  geom_point()


# night lights
#names(ndvi_zzc_stack) <- c(2014,2015,2016,2017)
avg_nl_zzc <- cellStats(nl_zzc_stack, mean)

avg_nl_zzc <- as_tibble(avg_nl_zzc)
# add a site column to our data


# add a "year" column to our data
avg_nl_zzc$'year' <- c(2014,2015,2016,2017)
hist(nl_zzc_stack)

avg_nl_zzc <- avg_nl_zzc[c("year", "value")]
avg_nl_zzc = rename(avg_nl_zzc, `meannl` = value)
avg_nl_zzc

ggplot(data = avg_nl_zzc, aes(x=year, y=meannl)) +
  geom_point()

```



## All four together

```{r}
#Taobao villages
ggplot(data = avg_ndvi_lbc, aes(x=year, y=meanndvi)) +
  geom_point()

ggplot(data = avg_ndvi_mdc, aes(x=year, y=meanndvi)) +
  geom_point()

ggplot(data = avg_ndvi_clc, aes(x=year, y=meanndvi)) +
  geom_point()

ggplot(data = avg_ndvi_zzc, aes(x=year, y=meanndvi)) +
  geom_point()


```




```{r}
hist(ndvi_lbc_stack)
hist(ndvi_mdc_stack)

hist(ndvi_clc_stack)
hist(ndvi_zzc_stack)



```
