---
title: "ds421 final project"
author: "xrw"
date: "5/3/2018"
output: pdf_document
---

#Contents

This is a final project PDF document for DS421 stitched together from other experiments in this rpo. 

Some major goals were:
- Get satellite data/imagery for village and county names.
- Poke around household income data
- Poke around land use change for a few Taobao villages. 

## Section A
First we'll take a look at household income data from CHIP, an{rd geocode the counties based off a csv of "official administrative codes".

We'll also poke at the data a bit, looking at changes over time.

## Section B


##CHIP

CHIP (China Household Income Project) is put out by the CIID Beijing as a longitudinal survey. It's been happening since 1988 and includes all kinds of juicy stuff including land use.

Load up necessary libraries. Some data is in `.dta` which is Stata file. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

```

```{r}
library(tidyr)
library(tidyverse)
library(dplyr)
library(foreign)
library(reticulate)
library(haven)

```


```{r}
chips_rur_1988 <- read_dta('data/1988/09836-0002-Data.dta')
chips_rur_1995 <- read_tsv('data/1995/DS0002/03012-0002-Data.tsv')
chips_rur_2002<- read_tsv('data/2002/DS0006/21741-0006-Data.tsv')
chips_rur_2007abc <- read_dta('data/2007 (2008)/RHS_w1_abc.dta')
chips_rur_2007d <- read_dta('data/2007 (2008)/RHS_w1_d.dta')
chips_rur_2007e1 <- read_dta('data/2007 (2008)/RHS_w1_e1.dta')
chips_rur_2007e2 <- read_dta('data/2007 (2008)/RHS_w1_e2.dta')
chips_rur_2007e3 <- read_dta('data/2007 (2008)/RHS_w1_e3.dta')
chips_rur_2007e4 <- read_dta('data/2007 (2008)/RHS_w1_e4.dta')
chips_rur_2007hhiexp <- read_dta('data/2007 (2008)/CHIP2007_income_and_expenditure_20150408.dta')
chips_rur_2008abc <- read_dta('data/2008 (2009)/RHS_w2_abc.dta')
chips_rur_2008d <- read_dta('data/2008 (2009)/RHS_w2_d.dta')
chips_rur_2008e <- read_dta('data/2008 (2009)/RHS_w2_e.dta')
chips_rur_2008f <- read_dta('data/2008 (2009)/RHS_w2_f.dta')
chips_rur_2008hgsg <- read_dta('data/2008 (2009)/RHS_w2_hgsg.dta')
chips_rur_2008hijk <- read_dta('data/2008 (2009)/RHS_w2_hijk.dta')
chips_rur_2008vill <- read_dta('data/2008 (2009)/RHS_w2_vill.dta')
chips_rur_2013 <- read_dta('data/2013/CHIP2013_rural_household_f_income_asset.dta')


```

```{r, echo=FALSE}
#Helper function for dta files


labelDataset <- function(data) {
  correctLabel <- function(x) {

    if(!is.null(attributes(x)$labels)) {
      class(attributes(x)$labels) <- typeof(x)
    }
    return(x)
  }

  for(i in colnames(data)) {
    data[, i] <- correctLabel(data[, i])
  }
  return(data)
}

#labelDataset(chips_rur_2007hhiexp)

```


### Table of columns used:

| Year | Net household income | Land cultivated | Number of rooms in House | Fixed production assets | Total household exp on production
|---|---|---|---|---|---|
|1988| HNET88 | LAT | HHO | VHPFP | EFP88 |
|1995| B602 | B801 | B1001 | B804_1 | B7130 |
|2002| na| na| na| na| na|
|2007| income_net | na | na | na | na|
|2009| na | H01 | na | K01 | na|
|2013| F01_1 | L01_1 | na | F07_1 + F07_2 | F02_1 | 


```{r}
# Filter out some data from 1988 because there's missing values. They got rid of missing values in later datasets.

chips_rur_1988_filt <- chips_rur_1988 %>% filter(HNET88 != 99999999, LAT != 999.9, HHO != 99, VHPFP != 99999, EFP88 != 99999999 ) 

base::mean(chips_rur_1988_filt$HNET88)
base::mean(chips_rur_1995$B602)
base::mean(chips_rur_2007hhiexp$income_net)
base::mean(chips_rur_2013$f01_1, na.rm=TRUE)




```


