---
title: "processing longlat coordinates to grab tiles, georeference and "
author: "Xiaowei Wang"
output: github_document
---



## Make bounding box off of one satellite tile.

bounding_box function is from https://github.com/trinker/bounding_box, an R implementation of Jan Philip Matuschek's algorithm. 

```{r}
bounding_box <- function(lat, lon, dist, in.miles = TRUE) {

    ## Helper functions
    if (in.miles) {
        ang_rad <- function(miles) miles/3958.756
    } else {
        ang_rad <- function(miles) miles/1000
    }
    `%+/-%` <- function(x, margin){x + c(-1, +1)*margin}
    deg2rad <- function(x) x/(180/pi)
    rad2deg <- function(x) x*(180/pi)
    lat_range <- function(latr, r) rad2deg(latr %+/-% r)
    lon_range <- function(lonr, dlon) rad2deg(lonr %+/-% dlon)

    r <- ang_rad(dist)
    latr <- deg2rad(lat)
    lonr <- deg2rad(lon)
    dlon <- asin(sin(r)/cos(latr))

    m <- matrix(c(lon_range(lonr = lonr, dlon = dlon), 
        lat_range(latr=latr, r=r)), nrow=2, byrow = TRUE)

    dimnames(m) <- list(c("lng", "lat"), c("min", "max"))
    m
}

```


```{r}

library(ggmap)
library(dismo)

#  test out the get map based on long lat

#libeicun 106.728735, 27.040506, this is one of the newest TBC
longitude_lb <- 106.728735
latitude_lb <- 27.040506

#madingcun 120.123507, 29.399521, change over multiple years, was in 2015 and 2016, not 2014
longitude_mdc <- 120.123507
latitude_mdc <- 29.399521


#安徽省程楼村 116.8437324, 34.2820951 not a TBC at all 

longitude_chengloucun <- 116.8437324
latitude_chengloucun <- 34.2820951


#浙江省紫竹村 zizhucun not a TBC at al 30.222385 119.378449
longitude_zzc <- 119.378449
latitude_zzc <- 30.222385

bbox_tile_plotter <- function (boundingbox, tile, longitude, latitude) {
      
    xmax <- boundingbox[1, 2] 
    ymin <- boundingbox[2,1]
    xmin <- boundingbox[1, 1]
    ymax <- boundingbox[2, 2]
      
      
     points_frame <- data.frame(lon = c(xmax, longitude, xmin),
                               lat = c(ymax, latitude, ymin),
                               name = c('max', 'center', 'min'))
      
          ggmap(tile, 
          extent="normal",
          ylab = "lat",
          xlab = "lon") +
        geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), color="red", fill=NA, size=2) +
      geom_point(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), size=5, color = "green") 
}

get_tile_save <- function (longitude, latitude, filename) {
  one_tile <- get_map(location = c(lon = longitude, lat = latitude), zoom = 16, maptype = "satellite")
  df <- data.frame(longitude, latitude)
  plot <- ggmap(one_tile, extent ="device") +
    geom_point(data=df,aes(x=longitude,y=latitude))
  
    ggsave(filename, plot, device='tiff')

    bb <- bounding_box(latitude, longitude, 0.62, in.miles=TRUE )
    
    bbox_tile_plotter(bb, one_tile, longitude, latitude)
    
}

#get_tile_save(longitude = longitude_lb, latitude = latitude_lb, filename = 'lb')
#get_tile_save(longitude = longitude_mdc, latitude = latitude_mdc, filename = 'mdc')
#get_tile_save(longitude = longitude_chengloucun, latitude = latitude_chengloucun, filename = 'mdc')
#get_tile_save(longitude = longitude_zzc, latitude = latitude_zzc, filename = 'zhizucun')
```







## Now let's georeference the satellite tile that we saved!

```{r}
#plot
#test_tile <- raster('a')
#extents <- c(xmin, xmax, ymin, ymax)
#setExtent(test_tile, extent(extents), keepres = FALSE, snap = FALSE )

#plot(test_tile)

```

## Well it turns out that there's an easier way to save geoTiffs and assign them a CRS... and that is using the dismo package in R!
```{r}



get_tile_save_geotiff <- function (long, lat, filename, zoom) {
    boundingbox <- bounding_box(lat, long, 0.62, in.miles=TRUE )
 
    xmax <- boundingbox[1, 2] 
    ymin <- boundingbox[2,1]
    xmin <- boundingbox[1, 1]
    ymax <- boundingbox[2, 2]

    
  extent_dismo <- extent(xmin, xmax, ymin, ymax)
  dismogmap_tile <- dismo::gmap(extent_dismo, type = 'satellite', zoom = zoom)
  plot(dismogmap_tile)
  projection(dismogmap_tile) <- CRS("+init=epsg:3857")
  writeRaster(dismogmap_tile, file = filename, format = "GTiff", overwrite = TRUE, 
    datatype = "INT1U")
}

get_tile_save_geotiff(longitude_zzc, latitude_zzc, 'dismo_zzc', zoom = 16)

```

## After getting the geoTiff tile, crop the raster files from landsat as well

```{r}

library(rgdal)
library(sp)

landsat <- brick('data/lbc-raster-cropped/lbc_2017_cropped.tif')
#this landsat image is from libeicun
crs(landsat)
#cropped <- crop(landsat, extent(dismogmap_tile), 'croppedlandsat')

make_a_bbox_shapefile <- function (long, lat, filename) {
  bb <- bounding_box(lat, long, 0.62, in.miles=TRUE )

  xmax <- bb[1, 2] 
  ymin <- bb[2,1]
  xmin <- bb[1, 1]
  ymax <- bb[2, 2]
      
  
  coords = matrix(c(xmax, ymax,
                xmin, ymax,
               xmin, ymin,
               xmax, ymin,
               xmax, ymax), 
             ncol = 2, byrow = TRUE)


  #Tryig out making a bounding box to a shapefile, to cross check with Google Earth and QGIS
  P1 <- Polygon(coords)
  Ps1 <- SpatialPolygons(list(Polygons(list(P1), ID = "a")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
  Ps2 <- as(Ps1, "SpatialPolygonsDataFrame")
  writeOGR(Ps2, filename, layer=filename, driver='ESRI Shapefile' )
}

#make_a_bbox_shapefile(longitude_mdc, latitude_mdc, filename = 'madingcun')
#make_a_bbox_shapefile(longitude_chengloucun, latitude_chengloucun, filename = 'chengloucun')
#make_a_bbox_shapefile(longitude_zzc, latitude_zzc, filename = 'zhizhucun' )

```

#Projections are off!

Landsat projection and making sure everything is same projection 
```{r}

#landsat: +proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0
#dismotile: +init=epsg:3857 +proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +no_defs
latt <- latitude_lb
longt <- longitude_lb

# longitude_chengloucun
#     boundingboxt <- bounding_box(latt, longt, 0.62, in.miles=TRUE )
#  
# 
#     txmax <- boundingboxt[1, 2] 
#     tymin <- boundingboxt[2,1]
#     txmin <- boundingboxt[1, 1]
#     tymax <- boundingboxt[2, 2]
# textent_dismo <- extent(txmin, txmax, tymin, tymax)
# dismogmapt_tile <- dismo::gmap(textent_dismo, type = 'satellite', zoom = 16)
# newproj <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
# dismogmap_tile_wgs <- projectRaster(dismogmapt_tile, crs = newproj)
# identicalCRS(dismogmapt_tile,landsat)
# 
# cropped <- crop(landsat, extent(dismogmap_tile_wgs))
# 
# plotRGB(cropped, r = 3, g = 2, b = 1, axes = TRUE, stretch = "lin",
#         main = "Landsat True Color Composite")
# 
# rf <- writeRaster(cropped, filename="data/lbc_2017_cropped.tif", format="GTiff", overwrite=TRUE)

```