---
title: "processing CHIPs data to get satellite imagery for the locations"
author: "Xiaowei Wang"
output: github_document
---


```{r}

library(haven)
# yourData = read_dta("CHIP2013_rural_household_f_income_asset.dta")
# yourData

# yourData2 = read_dta("RHS_w2_vill.dta")
# yourData3 = read_dta("RHS_w2_abc.dta")
# yourData4 = read_dta("RHS_w2_d.dta")
# yourData5 = read_dta("RHS_w2_e.dta")


# yourData2
# yourData3
# yourData4
# yourData5
```



```{r}
library(tidyverse)
# 2174 is CHIPS from 2002 
# for some reason this one has the clearest county level data
main_table_chips_2002 <- read_tsv('data/2002/DS0006/21741-0006-Data.tsv')
main_table_chips_1995 <- read_tsv('data/1995/DS0002/03012-0002-Data.tsv')
main_table_chips_1988 <- read_dta('data/1988/09836-0002-Data.dta')
main_table_chips_2008 <- read_dta("data/2008/RHS_w2_vill.dta")
main_table_chips_2013 <- read_dta("data/2013/CHIP2013_rural_household_f_income_asset.dta")


```

```{r}
#main_table_chips_2013$coun
setdiff(main_table_chips_1995$A1, main_table_chips_2002$coun)
#unique(main_table_chips_1995$A1)
#unique(main_table_chips_2002$coun)

ababa <- c(main_table_chips_2013$coun,main_table_chips_1995$A1,main_table_chips_2002$coun )
unique(ababa)
```

```{r}
# main_table_chips is a tale with 84 columns and 37969 rows
# the first column is county (coun), second column is vill (village), hous (is house)
```

# Get administrative divisions of China
```{r}
library(dplyr)

counties_main <- read_csv('https://raw.githubusercontent.com/modood/Administrative-divisions-of-China/master/dist/areas.csv')

counties_main
```

```{r}

#add long lat columns to the counties data

counties_main$lat <- 'NA'
counties_main$long <- 'NA'

city_main <- read_csv('https://raw.githubusercontent.com/modood/Administrative-divisions-of-China/master/dist/cities.csv')
province_main <- read_csv('https://raw.githubusercontent.com/modood/Administrative-divisions-of-China/master/dist/provinces.csv')

prov_county_main <- left_join(counties_main, province_main,
                              by=c('provinceCode'='code'))

prov_county_main <- prov_county_main %>%
    rename('cityName' = name.y, 
           'countyName' = name.x) %>%
    mutate(., geocodeAdd = paste0(cityName,countyName))


prov_county_main



```


```{r}

pcoun_codes_1 <- filter(prov_county_main, code < 400000)
pcoun_codes_2 <- filter(prov_county_main, code >= 400000)
```


#Grabbing the long lats from google maps

Example request:

##Geocoding
https://maps.googleapis.com/maps/api/geocode/json?address=1600+Amphitheatre+Parkway,+Mountain+View,+CA&key=YOUR_API_KEY

https://maps.googleapis.com/maps/api/geocode/json?address=辽宁省凤城市&key=AIzaSyAE8v4YljHZYZJ03VydAtAn5yNOGIfr50g 

##Static Map

https://maps.googleapis.com/maps/api/staticmap?center=40.452297,124.066919&zoom=16&size=400x400&maptype=satellite&key=AIzaSyDW8FM0kdCTFMF5iRO3z_tjWynVuzp8_iw

```{r}

# prov_county_main has the city and county data.
# concatenate the cityName and the countyName to feed in the address to google maps geocode api 

library(jsonlite)
library(httr)
library(ggmap)


```

```{r}

#Setting ggmap credentials here.
# If you have creds in your Renviron, then you don't need to set them

# ggmap_credentials()
# 
# register_google(key='')
# 
# ggmap_credentials()
# 
# library(ggmap)
# 
# ggmap_credentials()


```

```{r}

# 
# infile <- 'pcoun_2'
# data <-pcoun_codes_2
# 
# addresses = data$geocodeAdd
# 
# #define a function that will process googles server responses for us.
# getGeoDetails <- function(address){   
#    #use the gecode function to query google servers
#    geo_reply = geocode(address, output='all', messaging=TRUE, override_limit=TRUE)
#    #now extract the bits that we need from the returned list
# 
#    answer <- data.frame(lat=NA, long=NA, accuracy=NA, formatted_address=NA, address_type=NA, status=NA)
#    answer$status <- geo_reply$status
#  
#    #if we are over the query limit - want to pause for an hour
#    while(geo_reply$status == "OVER_QUERY_LIMIT"){
#        print("OVER QUERY LIMIT - Pausing for 1 hour at:") 
#        time <- Sys.time()
#        print(as.character(time))
#        Sys.sleep(60*60)
#        geo_reply = geocode(address, output='all', messaging=TRUE, override_limit=TRUE)
#        answer$status <- geo_reply$status
#    }
#  
#    #return Na's if we didn't get a match:
#    if (geo_reply$status != "OK"){
#        return(answer)
#    }   
#    #else, extract what we need from the Google server reply into a dataframe:
#    answer$lat <- geo_reply$results[[1]]$geometry$location$lat
#    answer$long <- geo_reply$results[[1]]$geometry$location$lng   
#    if (length(geo_reply$results[[1]]$types) > 0){
#        answer$accuracy <- geo_reply$results[[1]]$types[[1]]
#    }
#    answer$address_type <- paste(geo_reply$results[[1]]$types, collapse=',')
#    answer$formatted_address <- geo_reply$results[[1]]$formatted_address
#     
#    return(answer)
# }
#  
# #initialise a dataframe to hold the results
# geocoded <- data.frame()
# # find out where to start in the address list (if the script was interrupted before):
# startindex <- 1
# #if a temp file exists - load it up and count the rows!
# tempfilename <- paste0(infile, '_temp_geocoded.rds')
# if (file.exists(tempfilename)){
#        print("Found temp file - resuming from index:")
#        geocoded <- readRDS(tempfilename)
#        startindex <- nrow(geocoded)+1
#        print(startindex)
# }
#  
# # Start the geocoding process - address by address. geocode() function takes care of query speed limit.
# for (ii in seq(startindex, length(addresses))){
#    print(paste("Working on index", ii, "of", length(addresses)))
#    #query the google geocoder - this will pause here if we are over the limit.
#     
#    result = getGeoDetails(addresses[ii]) 
#    print(result$status)     
#    result$index <- ii
#    #append the answer to the results file.
#    geocoded <- rbind(geocoded, result)
#    #save temporary results as we are going along
#    saveRDS(geocoded, tempfilename)
# }

```

```{r}
# blar <- data.frame(matrix(ncol = 3, nrow = 1516))
# #now we add the latitude and longitude to the main data
# 
# blar$status <- geocoded$status
# blar$formatted_address <- geocoded$formatted_address
# blar$index <- geocoded$index
# blar$lat <- geocoded$lat
# blar$long <- geocoded$long
# blar$accuracy <- geocoded$accuracy
#  
# 
# 
# #finally write it all to the output files
# #saveRDS(data, paste0("../data/", infile ,"_geocoded.rds"))
# write.table(blar, file=paste0("", infile ,"_geocoded.csv"), sep=",", row.names=FALSE)

```

# Now there's two tables, put them together vertically

```{r}
a <- read_csv('data/pcoun_1_geocoded.csv')
b <- read_csv('data/pcoun_2_geocoded.csv')
geocoded_areas <- bind_rows(a,b)

prov_county_main$lat <- geocoded_areas$lat
prov_county_main$long <- geocoded_areas$long

prov_county_main$engAdd <- geocoded_areas$formatted_address
prov_county_main
```

```{r}

```

```{r}
# villages_main <- read_csv('../Administrative-divisions-of-China/dist/villages.csv')
# villages_main
# villages_main this is the list of villages, not necessarily helpful, wait for response from the chinese village researchers
```

```{r}

n <- left_join(main_table_chips_2002, prov_county_main, by=c('coun'='code'))


```


```{r}

n

```


```{r}
library(ggplot2)
library(ggmap)
library(dismo)
#  test out the get map based on long lat

#libeicun 106.728735, 27.040506
longcenter <- 106.728735
latcenter <- 27.040506


one_tile <- get_map(location = c(lon = longcenter, lat = latcenter), zoom = 16, maptype = "satellite") 

#df<-data.frame(longcenter,latcenter)
#       #a+ggplot(df) # Not sure what you intend here
plot <- ggmap(one_tile, extent ="device")+
  geom_point(data=df,aes(x=longcenter,y=latcenter))

# ggsave('aaaaaaa.tiff', device='tiff')



# final_map <- location +
#   geom_point(data = df, aes(x = longcenter, y = latcenter)) + 
#   theme(panel.border = element_blank(),
#         axis.title = element_blank(),
#         axis.text  = element_blank(),
#         axis.ticks = element_blank(),
#         plot.margin = unit(c(0,0,0,0), "cm"))

ggsave('a', plot, device='tiff')
```


## Make bounding box off of one satellite tile.

bounding_box function is from https://github.com/trinker/bounding_box, an R implementation of Jan Philip Matuschek's algorithm. 

```{r}
bounding_box <- function(lat, lon, dist, in.miles = TRUE) {

    ## Helper functions
    if (in.miles) {
        ang_rad <- function(miles) miles/3958.756
    } else {
        ang_rad <- function(miles) miles/1000
    }
    `%+/-%` <- function(x, margin){x + c(-1, +1)*margin}
    deg2rad <- function(x) x/(180/pi)
    rad2deg <- function(x) x*(180/pi)
    lat_range <- function(latr, r) rad2deg(latr %+/-% r)
    lon_range <- function(lonr, dlon) rad2deg(lonr %+/-% dlon)

    r <- ang_rad(dist)
    latr <- deg2rad(lat)
    lonr <- deg2rad(lon)
    dlon <- asin(sin(r)/cos(latr))

    m <- matrix(c(lon_range(lonr = lonr, dlon = dlon), 
        lat_range(latr=latr, r=r)), nrow=2, byrow = TRUE)

    dimnames(m) <- list(c("lng", "lat"), c("min", "max"))
    m
}



bb <- bounding_box(latcenter, longcenter, 0.62, in.miles=TRUE )

xmax <- bb[1, 2] 
ymin <- bb[2,1]
xmin <- bb[1, 1]
ymax <- bb[2, 2]


points_frame <- data.frame(lon = c(xmax, longcenter, xmin),
                           lat = c(ymax, latcenter, ymin),
                           name = c('max', 'center', 'min'))



ggmap(one_tile, 
      extent="normal",
      ylab = "lat",
      xlab = "lon") +
  	  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), color="red", fill=NA, size=2) +
      geom_point(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), size=5, color = "green")

      # geom_point(data=data.frame(lon = longcenter, lat = latcenter), size=7, color="yellow")
```


## Now let's georeference the satellite tile that we saved!

```{r}
plot
test_tile <- raster('a')

extents <- c(xmin, xmax, ymin, ymax)
setExtent(test_tile, extent(extents), keepres = FALSE, snap = FALSE )

#plot(test_tile)

```

## Well it turns out that there's an easier way to save geoTiffs and assign them a CRS...
```{r}

extent_dismo <- extent(xmin, xmax, ymin, ymax)

dismogmap_tile <- dismo::gmap(extent_dismo, type = 'satellite', zoom = 16)
dismogmap_tile

plot(dismogmap_tile)
projection(dismogmap_tile) <- CRS("+init=epsg:3857")
writeRaster(dismogmap_tile, file = "dismographtile_epsg", format = "GTiff", overwrite = TRUE, 
    datatype = "INT1U")

```

## After getting the geoTiff tile, crop the raster files from landsat as well

```{r}
landsat <- brick('data/imageToDriveExample.tif')
#this landsat image is from libeicun

cropped <- crop(landsat, extents, 'croppedlandsat')



```